---
title: "Intro to Shiny Practical 2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---

* Open the "prac3_shiny" vignette, and copy the code into an empty R file

```{r,eval=FALSE}
  vignette("prac3_shiny", package = "BristolVis")
```

.Large[
* Run the app to see what it does

* Add some text to the end of the sidebar to describe the dataset used 

* Add some text to the mainPanel() e.g. between the plot and the table

* Create a reactive expression so that the data does not have to be imported everytime the title is changed

* Re-run your app to ensure that it works as expected


## Build an app from scratch

Open a new Shiny app (File -> New File -> Shiny Web App. . .)

Develop an app to create reactive graph 

  * Use one of the layouts we discussed as part of this workshop
  
  * Load `shiny` and `ggplot2` packages
  
  * Load the `med` data set

  * Add some text to the app to describe the dataset used
   
  * Add at least one widget to the .cb[`sidebarPanel`] (but feel free to add as many as you like!)
   
  * Add some reative content (e.g. a plot or a table) to the .cb[`mainPanel`] that makes use of the input from your widget

Run the app to ensure that it works as expected.

---


## _Optional:_ Publish your app

* Ensure that your app.R file is contained within its own folder

* Deploy your app online
  * Go to [shinyapps.io](https://www.shinyapps.io/)
  * Follow the instructions there to publish your app



