---
title: "Intro to Shiny Practical 1"
output: html_document
---

Note: View this practical sheet online ([here](https://mcguinlu.github.io/slides/data_viz_short_course_shiny/pracs/practical_1.html)) to access the hints and tips.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Install and load packages


``` {r}
install.packages(c("shiny","ggplot2"))        

library(shiny)
library(ggplot2)

```

<hr>

## Warm-up: Run your first app

``` {r}
library(shiny)

ui <- fluidPage( 
  # Allow user to define two numbers
  numericInput(inputId = "add_1", label = "Number:", value = 0),
  numericInput(inputId = "add_2", label = "Number:", value = 0),
  # Display the output
  textOutput(outputId = "sum")
)
server <- function(input, output) {
  output$sum <- renderText({
    input$add_1 + input$add_2
  })
}
shinyApp(ui = ui, server = server)

```

__1.__ Copy the code above to an empty R file.

__2.__ Make sure you can run the app, both:

  * using CTRL+SHIFT+ENTER keyboard shortcut
  * from the console (note: you'll have to save it first)

<hr>

## Exercise 1: Design a user interface

__1.__ Open the `prac_1.R` file in the `shiny-practicals` folder. 

__2.__ Identify the opening and closing brackets of the elements of `sidebarLayout` (e.g. `sidebarLayout()`, `sidePanel()`, `mainPanel()`)

__3.__ Run the app to familiarise yourself with it

__4.__ Make the following changes:

* Change the title of the app to "Demo of a shiny app"

* Add a new `selectInput()` widget to the sidebar, with an inputId of "select", a label of "Choose one:", and choices of "sex","diet", and "status"

* Add a new `textInput()` widget to the sidebar with an inputId of "plottitle" and a label "Plot title:"

<details>
<summary>Hint</summary>
  
```{r}
selectInput(inputId = "select",
            label = "Choose one:",
            choices = c("sex","diet","status"))

textInput(inputId = "plottitle",
          label = "Plot title:")

```
  
</details>
<br>
  
__5.__ Re-run the app to ensure that the changes have worked

<hr>

## Exercise 2: Create reactive content

__1.__ Open the `prac_2.R` file in the `shiny-practicals` folder. 

__2.__ Run the app to familiarise yourself with it

__3.__ Examine the code used to produce the table in the UI/server

 * Why is the table not being displayed in the app?
 
 * Fix the code in the UI so that the table is displayed in the `mainPanel`
 
<details>
<summary>Hint</summary>

Remember that simply creating an object in the server using a `render*()` function doesn't automatically mean it is visible in the user interface. You need to pass the object, via it's outputId (in this case `"table"`), to the appropriate `*Output()` function.

```{r}
  tableOutput("table")
```
  
</details> 

<br>

__4.__ Examine the code used to produce the plot in the UI/server

 * Update the code so that the colour is set by the value of `input$pointcolour`
 
 * Update the code so that the title of the plot is defined by the value of the input from the `textInput()` widget
 
<details>
<summary>Hint</summary>

The colour is currently set to "diet" (`color = "diet"`), so you'll need to set it to use the value of `input$pointcolour`
  
Similarly, the value of the plot title is currently set to "Plot title" (`title = "Plot title"`), so you'll need to update this to use the value of the `inputText()` widget (i.e. `input$titletext`)  
  
</details> 
 
<br> 
 
__5.__ Re-run the app to ensure that the changes have worked