---
title: "Intro to Shiny Practical 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

Note: View this practical sheet online ([here](https://mcguinlu.github.io/slides/data_viz_short_course_shiny/pracs/practical_2.html)) to access the hints and tips.

## Exercise 3: Customising the UI

__1.__ Open the `prac_3.R` file in the `shiny-practicals` folder. 

__2.__ Run the app to see what it does

__3.__ Add some text to the end of the sidebar to describe the dataset used 

<details>
<summary>Hint</summary>
<hr>

In this session we spoke about using HTML tags to add (and format) text in your app. Why not try using a few to see what the different outputs look like?

```{r}
ui <- fluidPage(         
 h1("Header 1"),              # header (can be h1-h6)
 hr(),                        # horizontal rule
 br(),                        # line break
 p("Text"),                   # paragraph text
 p(strong("bold")),           # bold
 p(em("italic")),             # italics         
 p(code("code")),             # code highlighting         
 a(href="", "link"),          # Hyperlink            
 HTML("<p>Raw html</p>")      # Raw html                
)    
```  
  
<hr>  
</details>

<br>

__4.__ Add some text to the `mainPanel()` e.g. between the plot and the table

__5.__ Re-run your app to ensure that it works as expected

<hr>

## Exercise 4: The `reactive({})` function

In the previous session, we described an example where the data was being subset within the function that created the `barPlot` output object:

``` {r, eval = FALSE}
server <- function(input, output) {

 output$barPlot <- renderPlot({
      data <- head(med, n = input$slider) 
      
      ggplot(data = data, aes_string(fill = input$fill)) +
      geom_histogram(aes(x = status), stat = "count")
  })}
```

We converted this to the following code, using the `reactive({})` function, to prevent the data from being re-subset every time the user changed the value of `input$fill`:

``` {r, eval = FALSE}
server <- function(input, output) {
  data <- reactive({
        head(med, n = input$slider) 
  })

 output$barPlot <- renderPlot({
    ggplot(data = data(), aes_string(fill = input$fill)) +
      geom_histogram(aes(x = status), stat = "count")
  })}
``` 
  
Can you apply the same principle to the app in `prac_3.R`?

__1.__ In the the `prac_3.R`, create a reactive expression so that the data does not have to be subset every time the title of the plot is changed.

<hr>

## Exercise 5: Build an app from scratch

__1.__ Open a new Shiny app file in RStudio (File -> New File -> Shiny Web App. . .)

__2.__ Use one of the layouts we discussed as part of this workshop. 
  
  <details>
  <hr>
  <summary>Hint</summary>
  
  
  The default layout of new apps opened in RStudio is `sidebarLayout()`. Why not try switching to a different layout (e.g. `splitLayout()`)?
  
  <hr>  
    
  </details>
  
  <br>
  
__3.__ Load `shiny` and `ggplot2` packages
  
__4.__ Load the `med` data set
  
```{r}
med <- read.csv("http://bit.ly/bris-data-viz-med")
```

<br>

__5.__ Add some text to the app to describe the dataset used
  
<details>
<summary>Hint</summary>
<hr>

In this session we spoke about using HTML tags to add (and format) text in your app. Why not try using a few to see what the different outputs look like?

```{r}
ui <- fluidPage(         
 h1("Header 1"),              # header (can be h1-h6)
 hr(),                        # horizontal rule
 br(),                        # line break
 p("Text"),                   # paragraph text
 p(strong("bold")),           # bold
 p(em("italic")),             # italics         
 p(code("code")),             # code highlighting         
 a(href="", "link"),          # Hyperlink            
 HTML("<p>Raw html</p>")      # Raw html                
)    
```  
  
<hr>  
</details>

<br>
   
__6.__ Add at least one widget to the `sidebarPanel` (but feel free to add as many as you like!)
   
__7.__ Add some reactive content (e.g. a plot or a table) to the `mainPanel` that makes use of the input from your widget

__8.__ Run the app to ensure that it works as expected.

---


## Exercise 5: Publish your app [Optional]

__1.__ Ensure that your app.R file is contained within its own folder

__2.__ Deploy your app online

  * Go to [shinyapps.io](https://www.shinyapps.io/)
  
  * Follow the instructions there to publish your app



