---
title: "Intro to Shiny Practical 1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prac 1: Run your first app

``` {r}
library(shiny)

ui <- fluidPage( 
  # Allow user to define two numbers
  numericInput(inputId = "add_1", label = "Number:", value = 0),
  numericInput(inputId = "add_2", label = "Number:", value = 0),
  # Display the output
  textOutput(outputId = "sum")
)
server <- function(input, output) {
  output$sum <- renderText({
    input$add_1 + input$add_2
  })
}
shinyApp(ui = ui, server = server)

```

Make sure you can run it both:

  * from the console (note: you'll have to save it first)
  * using the "Run App" button

Add some code to show the result of subtracting the two numbers (hint: input$add_1 - input$add_2 )

---

## .yt[Your Turn: Design a user interface]
* Open the "prac1_shiny" , and copy the code into an empty R file


```{r,eval=FALSE}
  vignette("prac1_shiny", package = "BristolVis")
```

* Identify the opening and closing brackets of the elements of .cb[`sidebarLayout`] (e.g. .cb[sidebarLayout()], .cb[sidePanel()], .cb[mainPanel()])

* Run the app

* Make the following changes:
  * Change the title of the app to "Demo of a shiny app"
  * Add a new selectInput widget to the sidebar, with the options "sex","diet", and "status"
  * Add a new textInput widget to the sidebar with the label "Plot title:"
  
* What is the value of .cb[`input$textbox`] when the following is entered in it?  
_This is a test_    

---

## .yt[Your Turn: Create reactive content]

* Open the "prac2_shiny" vignette, and copy the code into an empty R file

```{r,eval=FALSE}

  vignette("prac2_shiny", package = "BristolVis")

```

* Run the app to familarise yourself with it

* Examine the code used to produce the table in the UI/server
  * Why is the table not being displayed in the app?
  * Fix the code in the UI so that the table is displayed in the .cb[`mainPanel`]

* Examine the code used to produce the plot in the UI/server
  * Update the code so that the colour is set by the value of .cb[`input$pointcolour`]
  * Update the code so that the title of the plot is defined by the value of the input from the .cb[`inputTextbox`] widget

* Re-run the app to ensure that the changes have worked